Exploring Science Fiction \& Fantasy Q/A

### 2020-02-17 Article_Final/main.tex

\subsection{Top questions}
\textbf{Assumption}: Write a pig script or MapReduce job to find top 10 title questions, identified by PostTypeID="1", in \textit{Posts.xml} based on the Score attribute. The result should be a list containing the top 10 questions, showing id, question, and score.\\ \\
\textbf{Implementation}: This mapper job functions similarly to 2c Top miners except it puts out 3 parsed attributes using the "triple"-mode of mapper\_core. The reducer performs the reduction and ordering, finding the 10 highest score values. It does this by inserting every input into a list instead of printing it, using pythons standard function string.sort to order it. It then iterates through the 10 highest values to give an output.\\ \\
\textbf{Notes/Reflection}: The reducer could potentially be improved by only keeping 10 elements in the list at once, changing them out as higher scores were encountered.
\lstinputlisting[firstline=1,lastline=10,title=2d\_output]{Code_output/output2d}

>>>>

\subsection{Top questions}
\textbf{Assumption}: Write a pig script or MapReduce job to find top 10 title questions, identified by PostTypeID="1", in \textit{Posts.xml} based on the Score attribute. The result should be a list containing the top 10 questions, showing id, question, and score.\\ \\
\textbf{Implementation}: This mapper job functions similarly to 2c Top users except it puts out 3 parsed attributes using the "triple"-mode of mapper\_core. The reducer performs the reduction and ordering, finding the 10 highest score values. It does this by inserting every input into a list instead of printing it, using pythons standard function string.sort to order it. It then iterates through the 10 highest values to give an output.\\ \\
\textbf{Notes/Reflection}: The reducer could potentially be improved by only keeping 10 elements in the list at once, changing them out as higher scores were encountered.
\lstinputlisting[firstline=1,lastline=10,title=2d\_output]{Code_output/output2d}
